### 2019-11-20 paper/paper.tex
Commit start LaTeX things, don't know what we need

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

\title{Cybercrime and Online Video Games}

\author{Emilio Lopez}
\affiliation{%
  \institution{Case Western Reserve University}
  \streetaddress{10900 Euclid Ave}
  \city{Cleveland}
  \country{Ohio}}
\email{eil11@case.edu}

\author{Cameron Hochberg}
\affiliation{%
  \institution{Case Western Reserve University}
  \streetaddress{10900 Euclid Ave}
  \city{Cleveland}
  \country{Ohio}}
\email{clh137@case.edu}

\author{Michael Silverman}
\affiliation{%
  \institution{Case Western Reserve University}
  \streetaddress{10900 Euclid Ave}
  \city{Cleveland}
  \country{Ohio}}
\email{mhs126@case.edu}

\author{Anthony Smith}
\affiliation{%
  \institution{Case Western Reserve University}
  \streetaddress{10900 Euclid Ave}
  \city{Cleveland}
  \country{Ohio}}
\email{aas182@case.edu}

%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Lopez, Hochberg, Silverman and Smith}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{web scraping, sentiment analysis, cybercrime}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigconf]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for all short- and
full-length articles, and optional for two-page abstracts.

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\linewidth]{sample-franklin}
%   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
%     Ewing, Inc. [Public domain], via Wikimedia
%     Commons. (\url{https://goo.gl/VLCRBB}).}
%   \Description{The 1907 Franklin Model D roadster.}
% \end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
{\bfseries also} include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed {\itshape below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, an article in a proceedings (of a conference,
  symposium, workshop for example) (paginated proceedings article)
  \cite{Andler79}, a proceedings article with all possible elements
  \cite{Smith10}, an example of an enumerated proceedings article
  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
  doctoral dissertation \cite{Clarkson85}, a master's thesis:
  \cite{anisi03}, an online document / world wide web resource
  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
  (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2019-11-20 paper/paper.tex
Update gitignore, start outlining paper

@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+  The growth of online video games has yielded a vast underground economy of
+  criminals who sell exploits and credentials to give gamers unfair advantages
+  in the games. This paper studies the sale of ``crimeware'' connected to
+  the Epic Games' ``Fortnite: Battle Royale'' video game. The authors created 
+  a webscraping tool to collect large amounts of data from a hacker forum to 
+  analyze key distributers in the economy.
 \end{abstract}
@@
 \section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+[INTRODUCE ONLINE VIDEO GAMES; TALK ABOUT SUCCESS AND VAST REACH]
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+[INTRODUCE HACKER FORUMS, SPECIFICALLY HACK FORUMS]
 
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
+\section{Background}
 
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
+\subsection{Fortnite: Battle Royale}
+[DISCUSS THE GAME IN LIGHT DETAIL; GENRE, PLAYER COUNT, DEMOGRAPHICS]
 
-\subsection{Template Styles}
+\subsection{Hack Forums}
+[DISCUSS HACK FORUMS]
 
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
+\subsection{Web Scraping}
+[DISCUSS PURPOSE OF WEB SCRAPING]
 
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
+\subsection{Sentiment Analysis}
+[DISCUSS AI AND SETINMENT ANALYSIS]
 
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
+\section{Method}
 
-\subsection{Template Parameters}
+[DISCUSS IMPLEMENTATION OF OUR WEB SCRAPER]
 
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
+[DISCUSS OUR TECHNIQUE OF DATA ANALYSIS]
 
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
+\section{Evaluation}
 
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigconf]{acmart}
-\end{verbatim}
+% The title of your work should use capital letters appropriately -
+% \url{https://capitalizemytitle.com/} has useful rules for
+% capitalization. Use the {\verb|title|} command to define the title of
+% your work. If your work has a subtitle, define it with the
+% {\verb|subtitle|} command.  Do not insert line breaks in your title.
 
-\section{Modifications}
+% If your title is lengthy, you must define a short version to be used
+% in the page headers, to prevent overlapping text. The \verb|title|
+% command has a ``short title'' parameter:
+% \begin{verbatim}
+%   \title[short title]{full title}
+% \end{verbatim}
 
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
+% Above was too helpful to uncomment
 

### 2019-12-04 paper/paper.tex
Add to outline

@@
 \begin{abstract}
+  [REWRITE THIS AT END]
   The growth of online video games has yielded a vast underground economy of
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{web scraping, sentiment analysis, cybercrime}
+\keywords{web scraping, sentiment analysis, cybercrime, video games}
 
@@
 
-[INTRODUCE ONLINE VIDEO GAMES; TALK ABOUT SUCCESS AND VAST REACH]
+[INTRODUCE ONLINE VIDEO GAMES; TALK ABOUT SUCCESS AND LARGE APPEAL]
 
-[INTRODUCE HACKER FORUMS, SPECIFICALLY HACK FORUMS]
+[INTRODUCE CONCEPT OF HACKER FORUMS]
 
@@
 
-[DISCUSS OUR TECHNIQUE OF DATA ANALYSIS]
+[DISCUSS OUR TECHNIQUE OF DATA ANALYSIS - i.e, sentiment analyze all, then manually confirm other details]
 
-\section{Evaluation}
+\section{Results}
 
@@
 % Above was too helpful to uncomment
+[RAW RESULTS DATA, THEN REFINED DATA]
 
-\section{Authors and Affiliations}
+\subsection{Key Players}
+[A table would be a nice addition here]
+[DISCUSS THE DIFFERENT KEY MEMBERS OF THE COMMUNITY]
+[WHICH CHEATS ARE MOST POPULAR]
 
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
+\section{Solutions}
+\subsection{Video Game Cheats}
+[MIN 1 PARA PER OUR SOLUTIONS, EXPLAINING WHY ADDRESSES]
 
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
+\subsection{Account Theft}
+[MFA (already in Fortnite) but suggest mandating it]
+[FIND STATS OF HOW IT REDUCES BREACHES]
 
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
+\section{Conclusion}
+[CONCLUDE]
+[ALSO DISCUSS WHAT WE LEARNED (I think she wants that...)]
 
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
+% Information on how to make tables
 
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
+% \section{Tables}
 
-\section{Rights Information}
+% The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
+% package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
+% high-quality tables.
 
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
+% Table captions are placed {\itshape above} the table.
 
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
+% Because tables cannot be split across pages, the best placement for
+% them is typically the top of the page nearest their initial cite.  To
+% ensure this proper ``floating'' placement of tables, use the
+% environment \textbf{table} to enclose the table's contents and the
+% table caption.  The contents of the table itself must go in the
+% \textbf{tabular} environment, to be aligned properly in rows and
+% columns, with the desired horizontal and vertical rules.  Again,
+% detailed instructions on \textbf{tabular} material are found in the
+% \textit{\LaTeX\ User's Guide}.
 
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
+% Immediately following this sentence is the point at which
+% Table~\ref{tab:freq} is included in the input file; compare the
+% placement of the table here with the table in the printed output of
+% this document.
 
-\section{CCS Concepts and User-Defined Keywords}
+% \begin{table}
+%   \caption{Frequency of Special Characters}
+%   \label{tab:freq}
+%   \begin{tabular}{ccl}
+%     \toprule
+%     Non-English or Math&Frequency&Comments\\
+%     \midrule
+%     \O & 1 in 1,000& For Swedish names\\
+%     $\pi$ & 1 in 5& Common in math\\
+%     \$ & 4 in 5 & Used in business\\
+%     $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+%   \bottomrule
+% \end{tabular}
+% \end{table}
 
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
+% To set a wider table, which takes up the whole width of the page's
+% live area, use the environment \textbf{table*} to enclose the table's
+% contents and the table caption.  As with a single-column table, this
+% wide table will ``float'' to a location deemed more
+% desirable. Immediately following this sentence is the point at which
+% Table~\ref{tab:commands} is included in the input file; again, it is
+% instructive to compare the placement of the table here with the table
+% in the printed output of this document.
 
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
+% \begin{table*}
+%   \caption{Some Typical Commands}
+%   \label{tab:commands}
+%   \begin{tabular}{ccl}
+%     \toprule
+%     Command &A Number & Comments\\
+%     \midrule
+%     \texttt{{\char'134}author} & 100& Author \\
+%     \texttt{{\char'134}table}& 300 & For tables\\
+%     \texttt{{\char'134}table*}& 400& For wider tables\\
+%     \bottomrule
+%   \end{tabular}
+% \end{table*}
 
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
+% In case we want to add figures to our paper
+% \section{Figures}
 
-CCS concepts and user-defined keywords are required for all short- and
-full-length articles, and optional for two-page abstracts.
+% The ``\verb|figure|'' environment should be used for figures. One or
+% more images can be placed within a figure. If your figure contains
+% third-party material, you must clearly identify it as such, as shown
+% in the example below.
+% % \begin{figure}[h]
+% %   \centering
+% %   \includegraphics[width=\linewidth]{sample-franklin}
+% %   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
+% %     Ewing, Inc. [Public domain], via Wikimedia
+% %     Commons. (\url{https://goo.gl/VLCRBB}).}
+% %   \Description{The 1907 Franklin Model D roadster.}
+% % \end{figure}
 
-\section{Sectioning Commands}
+% Your figures should contain a caption which describes the figure to
+% the reader. Figure captions go below the figure. Your figures should
+% {\bfseries also} include a description suitable for screen readers, to
+% assist the visually-challenged to better understand your work.
 
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
+% Figure captions are placed {\itshape below} the figure.
 
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
+% \subsection{The ``Teaser Figure''}
 
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-% \begin{figure}[h]
-%   \centering
-%   \includegraphics[width=\linewidth]{sample-franklin}
-%   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-%     Ewing, Inc. [Public domain], via Wikimedia
-%     Commons. (\url{https://goo.gl/VLCRBB}).}
-%   \Description{The 1907 Franklin Model D roadster.}
-% \end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\itshape below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
+% A ``teaser figure'' is an image, or set of images in one figure, that
+% are placed after all author and affiliation information, and before
+% the body of the article, spanning the page. If you wish to have such a
+% figure in your article, place the command immediately before the
+% \verb|\maketitle| command:
+% \begin{verbatim}
+%   \begin{teaserfigure}
+%     \includegraphics[width=\textwidth]{sampleteaser}
+%     \caption{figure caption}
+%     \Description{figure description}
+%   \end{teaserfigure}
+% \end{verbatim}
 
@@
 
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
 %%
@@
 \begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
 \end{acks}
@@
 
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
 \end{document}

### 2019-12-05 paper/paper.tex
Start writing some sections

@@
 \subsection{Web Scraping}
-[DISCUSS PURPOSE OF WEB SCRAPING]
+Web scraping refers to the process of extracting data from web pages, and the 
+term typically implies the automation of this process. Data extracted from web
+pages will then be parsed to be usable. Often, websites will not provide 
+easily accessible data sets of the website content, which means that a 
+web scraping program must be written to extract the relevant information from
+the HTML present on the page.
 
@@
 
-[DISCUSS IMPLEMENTATION OF OUR WEB SCRAPER]
+\subsection{Web Scraper Implementation}
+We opted to implement our web scraping program in the Python 3 programming
+language. Given the time constraints of the project, we found that Python
+matched our needs well given its rapid development time. In addition, the 
+external library support of Python was deemed essential in traversing
+Hack Forums and extracting the data. We also used Selenium web automation tool
+and its relevant Python bindings. For Python, we also used the "Requests" and 
+"BeautifulSoup" libraries. "Requests" simplifies the creation of HTTP requests 
+to obtain web content, and "BeautifulSoup" is an HTML parser which assists
+in unraveling the web page content to extract. Finally, to actually create
+the requisite Excel file, we used the OpenPyXL library to generate and
+populate the file.
+
+Since the program's scraping is based on the website's specific content and 
+design (e.g., names of tag classes and id attributes in the page HTML), the web
+scraper can only be used for Hack Forums. Hack Forums provided some unique
+challenges for our scraping. For example, the website seems to heavily rely
+on the PHP programming language. For searching the forum threads, this is 
+troublesome, because the search itself is not a simple web endpoint where the 
+search term can be replaced. This design decision requires the use of Selenium
+to "click" buttons and enter search terms into the website's forms. For each
+page of search results, the URL for the thread is acquired along with the 
+original poster, number of replies, and other relevant information. With the 
+URL for a thread, the comment pages are requested and the relevant information
+per comment is scraped from each page for the thread.
+
+After all the is collected from a search, the data is written to an Excel file
+which contains all the results. With all the data aggregated, manual data
+analysis can begin.
 
@@
 [RAW RESULTS DATA, THEN REFINED DATA]
+[TABLES WOULD BE HELPFUL HERE]
 

### 2019-12-05 paper/paper.tex
more paper, add the pdf to ignore

@@
 \subsection{Hack Forums}
-[DISCUSS HACK FORUMS]
+There exist many forums on the Internet for persons interested in computer
+hacking, but one the most visited is Hack Forums (hackforums.net). Ranked
+second in top sites for "hacking" (https://www.alexa.com/topsites/category/Top/Computers/Hacking), Hack Forums has several discussion boards
+on topics ranging from social engineering techniques to Internet-of-Things 
+exploits. On Hack Forums, users make accounts to use the community forums:
+posting, searching, and even browsing requires an account to be registered.
+Users also can give feedback on each other. For example, a user with
+a high feedback score will be regarded as more trustworthy. Often, these users
+gain repute by participating in discussion or selling a legitimate product or 
+service. Users can also privately message each other, without having to use
+another service like email. Due to Hack Forums' prominence and enablement of 
+cybercrime, it merited our scrutiny to examine its contribution to cybercrime
+in the video game space.
 
@@
 [DISCUSS AI AND SETINMENT ANALYSIS]
+
+\section{Crimeware}
+
+\subsection{Video Game Cheats}
+
+\subsection{Account Sales}
 

### 2019-12-05 paper/paper.tex
Minor additions to Web Scraping background
Add a lot to the paper

@@
 %%
+% i never got this to work
 \begin{CCSXML}
@@
 \subsection{Fortnite: Battle Royale}
-[DISCUSS THE GAME IN LIGHT DETAIL; GENRE, PLAYER COUNT, DEMOGRAPHICS]
+Developed by Epic Games, "Fortnite: Battle Royale" or "Fortnite" is a 
+third-person shooter and battle royale online video game. The player must
+utilize a diverse arsenal of weapons to defeat 99 other human opponents and 
+claim victory.
 
@@
 hacking, but one the most visited is Hack Forums (hackforums.net). Ranked
-second in top sites for "hacking" (https://www.alexa.com/topsites/category/Top/Computers/Hacking), Hack Forums has several discussion boards
+second in top sites for "hacking" % (https://www.alexa.com/topsites/category/Top/Computers/Hacking), Hack Forums has several discussion boards
 on topics ranging from social engineering techniques to Internet-of-Things 
@@
 web scraping program must be written to extract the relevant information from
-the HTML present on the page.
+the HTML present on the page. Given the sheer volume of information that must
+be collected, the best action is to implement our own program to scrape data 
+from Hack Forums.
 
@@
 
+However, the data analysis for sentiment does not always apply to the comment.
+For example, if the comment is actually a question or a request to receive a 
+private message, then AI sentiment analysis of the comment is likely irrelevant.
+Therefore, the comments must be analyzed for different criteria. For example, 
+if the comment is actually a user "bumping" the thread, then it should be 
+discarded. It was not feasible for us to develop an AI solution to accurately
+categorize comments in each possible scenario, so we have chosen to automate
+the collection of data but manually classify it.
+
 \section{Results}
@@
 \subsection{Account Theft}
-[MFA (already in Fortnite) but suggest mandating it]
-[FIND STATS OF HOW IT REDUCES BREACHES]
+% [MFA (already in Fortnite) but suggest mandating it]
+Given the prominence of account theft and sales, we propose that Fortnite -
+and other online video games like it - mandate the use of multi-factor
+authentication (MFA) in combination with username and password credentials to
+secure accounts. Epic Games has already implemented an MFA tool for players to 
+use to protect their accounts, and the game incentivizes players to use it;
+however, we argue that optional usage of MFA is insufficient, and that online 
+video game developers should require the usage of MFA as part of accessing one's
+account. Additionally, we suggest that video game developers create their own 
+solution instead of relying on a simple SMS numerical code. SMS messages can be 
+intercepted, and an attacker can actually acquire the code for login. However,
+a robust, novel implementation can likely thwart the majority of hackers and 
+provide for the safety of a user's account.
+
+% [FIND STATS OF HOW IT REDUCES BREACHES]
+% https://security.googleblog.com/2019/05/new-research-how-effective-is-basic.html
 

### 2019-12-11 paper/paper.tex
Sentiment Analysis + start of video game cheats

@@
 \subsection{Sentiment Analysis}
-[DISCUSS AI AND SETINMENT ANALYSIS]
+One of our tasks was to analyze the intentions behind each comment, whether
+they were criticizing the product or, on the contrary, if they were lauding
+the product. For that, we decided to use a Python package provided by scikit-learn.org
+We used 3 different machine learning techniques to classify each comment as
+either positive or negative: Stochastic Gradient Descent (SGD), Naive Bayes, 
+Support Vector machines (SVC).
+Each algorithm gives each comment a probability to be either positive or negative.
+We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral.
 
@@
 \subsection{Video Game Cheats}
+
+\subsubsection(Aimbots)
+Aimbots are a sub set of game hacks. These reffer to scripts that run on the client side of the game 
+and track things such as hit boxes of other players in the game and aim for you once activated. It is 
+an easy kind of cheat to spot as it will usually result in unhuman reflexes or movement or such things 
+as wall tracking where a player is aiming at you through a wall. Since they also track only specific 
+areas, a statistical analysis of the areas where the player regularly hit his targets can reveal whether 
+or not he was hacking. Normal humans can't aim at the same target over a long period of time and will
+usually stay within one or two standard deviations of the mean for any given area. Someone who aimbots 
+on the other hand will usually have one area that is way above the mean.
+
+\subsubsection (Wall Hacks)
+There are several versions of this cheat but there is usually two types: a script that uses a bug from the
+developer to allow the user to view more than he should be making walls transparent or "see-through"; another would be to make walls non solid objects allowing the player to shoot through walls or even hide in them.
+These hacks usually relly on the fact the FPS games in particular send only the raw positional information of players and let the player or client's 3D renderer to hide other players behind walls or through "fog of war".
+These can be turned off from the client side and thus make it look like the players are moving around what seams like an empty space.
+Obviously a completely empty map serves no purpose for the hacker as he couldn't navigate the map properly either.
+This third party software allows the user to only hide certain surfaces from its client 3D renderer so that the hacker may have an edge compared to other players.
+
+\subsubsection(Nuking or artificial lag)
+The sub genre of hacks, as its name suggests, consists of artificially generating lag between the client and the server in order to gain an advantage.
+In some games, hits aren't registered until the server registeres a hit.
 

### 2019-12-12 paper/paper.tex
Update paper.tex

@@
 \subsection{Key Players}
-[A table would be a nice addition here]
-[DISCUSS THE DIFFERENT KEY MEMBERS OF THE COMMUNITY]
-[WHICH CHEATS ARE MOST POPULAR]
+In the context of our project, the key players in the Fortnite hacker forums are those who have the most threads and/or comments under their names.
+We defined a user as a key player if they posted more than one thread or more than fifty comments from our 104 threads and 7932 comments.
+We determined these metrics by manually analyzing the comments and threads and determining who were the minority of more active users.
+These active user threads will usually take the form of either crimeware or CaaS with the poster selling to whoever can pay with some supposedly “legal” methods scattered throughout.
+Some of the more popular services are account selling, radar hacks, aimbot hacks and cheaper V-Bucks.
+Below are two pie charts depicting the thread and comment counts with the labels identifying the greater contributors.
+
+\subsubsection{Wyattz}
+Wyattz can be considered the most active user on the Fortnite hacker forums being tied for the most threads at three and having the most comments at 162.
+Wyattz is also a veteran member of hackforums.net and appears to be a trusted source of “legal” software and methods.
+His Fortnite posts revolve around making money playing Fortnite using what he claims to be a legal method.
+Since we were unable to access his method we could not determine its legality but his customers have commented back with general satisfaction.
+The other factor that makes Wyattz interesting is his number of comments.
+These comments were not made on other threads but on his own.
+His comments are either responses to other user’s comments or simply declarations that he is online and ready to talk.
+Wyattz places a lot of effort into his work on hackerforum so even though his comments rarely range outside his own threads and his product is not explicitly illegal, he is still a major player worth looking at.
+
+\subsubsection{Jombah}
+Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and ___ comments.
+He still passes the threshold for being a key player but the reason he is being focused on is due to his product.
+Jombah sells Fortnite accounts which is one of the crimewares we are focusing on.
+Jombah’s products are “premium” accounts which he appears to sell for a relatively cheap price as compared to other sellers though unlike some other sellers he does not offer custom accounts that a buyer can specify.
+Jombah is also a decently active user on hackerforum.net though not as active as Wyattz or as well liked by his customers.
+Jombah’s relevance lies not with his stellar service but with the product he provides.
+
+\subsubsection{Dylan}
+The last key player we will feature is probably the most important figure in the overall Fortnite hackforum community, though that is not saying much.
+Dylan provides the cheats for users such as radar and silencers.
+His presentation and communication with clients is professionally done and there are very few complaints regarding his product.
+While this is important for Dylan’s hierarchy as a key player, what is most important about him is that he interacts with other Fortnite posters.
+While analyzing threads and comments, we noticed that very few posters comment beyond their threads.
+There is little to no communication among the Fortnite hackforum community.
+Dylan is the exception to the rule.
+He comments on other threads whether he is providing explanations of services, vouching for others or shooting down fraudulent products.
+Dylan is not the most active user in his community, but nobody is as far reaching making him the most important key player in this community.
+
+%[A table would be a nice addition here]
+%[DISCUSS THE DIFFERENT KEY MEMBERS OF THE COMMUNITY]
+%[WHICH CHEATS ARE MOST POPULAR]
 

### 2019-12-12 paper/paper.tex
Update paper.tex

@@
 
+\subsection{Key Players Conclusion}
+After analyzing the comments and threads we formed a decent understanding of the hackforum Fortnite community.
+The community doesn’t appear to revolve around any given person or group with many independent people providing products and/or services to Fortnite players.
+Even the most active figures in the community don’t communicate with each other in general.
+The Fortnite threads almost cannot be considered a community, more like a loose collection of people with similar ideas.
+This makes the key players less important as nobody has control over any aspect of the community.
+
 %[A table would be a nice addition here]

### 2019-12-13 paper/paper.tex
Update paper.tex
Modify some sections, comment the figure inclusion to allow compilation

@@
 %%\citestyle{acmauthoryear}
+
+\usepackage{graphicx}
 
@@
 
-\subsubsection(Aimbots)
+\subsubsection{Aimbots}
 Aimbots are a sub set of game hacks. These reffer to scripts that run on the client side of the game 
@@
 
-\subsubsection (Wall Hacks)
+\subsubsection{Hacks}
 There are several versions of this cheat but there is usually two types: a script that uses a bug from the
@@
 
-\subsubsection(Nuking or artificial lag)
+\subsubsection{Nuking or artificial lag}
 The sub genre of hacks, as its name suggests, consists of artificially generating lag between the client and the server in order to gain an advantage.
@@
 
+% this is not compiling
+
+% \begin{figure}
+% \centering
+% \begin{subfigure}{.5\textwidth}
+% 	\centering
+% 	\includegraphics[width = .4\linewidth]{ThreadCount}
+% 	\caption{Thread Count}
+% 	\label{fig:thread count}
+% \end{subfigure}
+% \begin{subfigure}{.5\textwidth}
+% 	\centering
+% 	\includegraphics[width=.4\linewidth]{Comment Count}
+% 	\caption{Comment Count}
+% 	\label{fig:comment count}
+% \end{subfigure}
+% \caption{Thread and Comment Pie Charts}
+% \label{fig:thread and comment charts}
+% \end{figure}
+
 \subsubsection{Wyattz}
@@
 \subsubsection{Jombah}
-Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and ___ comments.
+Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and [NUMBER] comments.
 He still passes the threshold for being a key player but the reason he is being focused on is due to his product.

### 2019-12-13 paper/paper.tex
Update paper.tex

@@
 % 	\centering
-% 	\includegraphics[width = .4\linewidth]{ThreadCount}
+% 	\includegraphics[width = .4\linewidth]{Thread Count}
 % 	\caption{Thread Count}
-% 	\label{fig:thread count}
 % \end{subfigure}
@@
 % 	\caption{Comment Count}
-% 	\label{fig:comment count}
 % \end{subfigure}
@@
 \subsubsection{Jombah}
-Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and [NUMBER] comments.
+Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and 43 comments.
 He still passes the threshold for being a key player but the reason he is being focused on is due to his product.

### 2019-12-13 paper/paper.tex
Update paper.tex
Delete paper.pdf since it generates, add my introduction changes for real

@@
 
-[INTRODUCE ONLINE VIDEO GAMES; TALK ABOUT SUCCESS AND LARGE APPEAL]
-
-[INTRODUCE CONCEPT OF HACKER FORUMS]
+Since their inception decades ago, video games have become hugely preavalent in
+society. Millions of people play video games as a hobby, and their demographics
+span all age groups, ethnicities, and socioeconomic class. In particular, online
+multiplayer video games have become hugely popular. Many of these games are 
+highly competitive, and there any many players who look for unfair advantages in
+the form of video game cheats. Video game cheats give the player abilities to 
+to outperform their opponents. This competitive milieu has led to the
+development of thriving marketplaces and economies devoted to creation and 
+distribution of video game cheats. Online hacker forums are places where 
+interested parties can sell, discuss, and review video game cheats. However, 
+these vendors not only sell cheats but also online video game accounts. These
+are especially desirable to perons who have been forbidden from playing an 
+online game by the developers - usually for cheating or other malicious
+behavior. Often, these accounts are stolen from innocent users and sold to 
+malicious actors. Many of the players of online video games are 
+children, and thus they are often the victims of account theft. This paper 
+explores the crimware economy devoted to "Fortnite: Battle Royale."
 
@@
 
-% this is not compiling
-
-% \begin{figure}
-% \centering
-% \begin{subfigure}{.5\textwidth}
-% 	\centering
-% 	\includegraphics[width = .4\linewidth]{Thread Count}
-% 	\caption{Thread Count}
-% \end{subfigure}
-% \begin{subfigure}{.5\textwidth}
-% 	\centering
-% 	\includegraphics[width=.4\linewidth]{Comment Count}
-% 	\caption{Comment Count}
-% \end{subfigure}
-% \caption{Thread and Comment Pie Charts}
-% \label{fig:thread and comment charts}
-% \end{figure}
+\begin{figure}
+\centering
+\begin{subfigure}{.5\textwidth}
+ 	\centering
+	\includegraphics[width = .4\linewidth]{ThreadCount}
+	\caption{Thread Count}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+ 	\centering
+	\includegraphics[width=.4\linewidth]{CommentCount}
+	\caption{Comment Count}
+\end{subfigure}
+\caption{Thread and Comment Pie Charts}
+\end{figure}
 

### 2019-12-13 paper/paper.tex
Added bibliography start + start solutions

@@
 There are several versions of this cheat but there is usually two types: a script that uses a bug from the
-developer to allow the user to view more than he should be making walls transparent or "see-through"; another would be to make walls non solid objects allowing the player to shoot through walls or even hide in them.
-These hacks usually relly on the fact the FPS games in particular send only the raw positional information of players and let the player or client's 3D renderer to hide other players behind walls or through "fog of war".
-These can be turned off from the client side and thus make it look like the players are moving around what seams like an empty space.
-Obviously a completely empty map serves no purpose for the hacker as he couldn't navigate the map properly either.
-This third party software allows the user to only hide certain surfaces from its client 3D renderer so that the hacker may have an edge compared to other players.
+developer to allow the user to view more than he should be making walls transparent or "see-through"; 
+another would be to make walls non solid objects allowing the player to shoot through walls or 
+even hide in them. These hacks usually relly on the fact the FPS games in particular send 
+only the raw positional information of players and let the player or client's 3D renderer to 
+hide other players behind walls or through "fog of war". These can be turned off from the client 
+side and thus make it look like the players are moving around what seams like an empty space. 
+Obviously a completely empty map serves no purpose for the hacker as he couldn't navigate the map properly 
+either. This third party software allows the user to only hide certain surfaces from its client 3D 
+renderer so that the hacker may have an edge compared to other players.
 
 \subsubsection{Nuking or artificial lag}
-The sub genre of hacks, as its name suggests, consists of artificially generating lag between the client and the server in order to gain an advantage.
-In some games, hits aren't registered until the server registeres a hit.
+The sub genre of hacks, as its name suggests, consists of artificially generating lag between the 
+client and the server in order to gain an advantage. In some games, hits aren't registered until 
+the server registeres a hit. In this case, overloading the server with packets just enough to create lag
+for every player on the server but not enough to cause the server to crash allows you to stall the game
+enough for you to be able to win effortlessly in the next round.
 
@@
 \subsection{Video Game Cheats}
-[MIN 1 PARA PER OUR SOLUTIONS, EXPLAINING WHY ADDRESSES]
+\subsubsection{Mirrored server design}
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{paper}{}
 

### 2019-12-13 paper/paper.tex
Add acknowledgements

@@
 
-\section{Citations and Bibliographies}
+% \section{Citations and Bibliographies}
 
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
+% The use of \BibTeX\ for the preparation and formatting of one's
+% references is strongly recommended. Authors' names should be complete
+% --- use full first names (``Donald E. Knuth'') not initials
+% (``D. E. Knuth'') --- and the salient identifying features of a
+% reference should be included: title, year, volume, number, pages,
+% article DOI, etc.
 
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
+% The bibliography is included in your source document with these two
+% commands, placed just before the \verb|\end{document}| command:
+% \begin{verbatim}
+%   \bibliographystyle{ACM-Reference-Format}
+%   \bibliography{bibfile}
+% \end{verbatim}
+% where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
+% suffix, of the \BibTeX\ file.
 
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
+% Citations and references are numbered by default. A small number of
+% ACM publications have citations and references formatted in the
+% ``author year'' style; for these exceptions, please include this
+% command in the {\bfseries preamble} (before
+% ``\verb|\begin{document}|'') of your \LaTeX\ source:
+% \begin{verbatim}
+%   \citestyle{acmauthoryear}
+% \end{verbatim}
 
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
-  doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
+%   Some examples.  A paginated journal article \cite{Abril07}, an
+%   enumerated journal article \cite{Cohen07}, a reference to an entire
+%   issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
+%   monograph/whole book in a series (see 2a in spec. document)
+%   \cite{Harel79}, a divisible-book such as an anthology or compilation
+%   \cite{Editor00} followed by the same example, however we only output
+%   the series if the volume number is given \cite{Editor00a} (so
+%   Editor00a's series should NOT be present since it has no vol. no.),
+%   a chapter in a divisible book \cite{Spector90}, a chapter in a
+%   divisible book in a series \cite{Douglass98}, a multi-volume work as
+%   book \cite{Knuth97}, an article in a proceedings (of a conference,
+%   symposium, workshop for example) (paginated proceedings article)
+%   \cite{Andler79}, a proceedings article with all possible elements
+%   \cite{Smith10}, an example of an enumerated proceedings article
+%   \cite{VanGundy07}, an informally published work \cite{Harel78}, a
+%   doctoral dissertation \cite{Clarkson85}, a master's thesis:
+%   \cite{anisi03}, an online document / world wide web resource
+%   \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
+%   \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
+%   (Case 3) a patent \cite{JoeScientist001}, work accepted for
+%   publication \cite{rous08}, 'YYYYb'-test for prolific author
+%   \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
+%   contain 'duplicate' DOI and URLs (some SIAM articles)
+%   \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
+%   multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
+%   couple of citations with DOIs:
+%   \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
+%   citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
+%   \cite{R} and \cite{UMassCitations}.
 
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
 \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
+  We would like to thank Professor Yanfang "Fanny" Ye of Case Western Reserve
+  University for assisting us with the completion of our project. The guidance
+  helped to refine the direction of our research and focus. With her assistance,
+  we found a novel concept to explore.
 \end{acks}

### 2019-12-13 paper/paper.tex
updated solutions + bibliography

@@
 
+\subsubsection{Code Injection}
+"Code Injection is the general term for attack types which consist of injecting code that is then 
+interpreted/executed by the application."\cite{codeinjection}
+Usually these attacks are the result of poor data validation from input/output. Code Injection deffiers from
+Command Injection in the sense that the attacker, in the case of Command Injection, is limited by what the API
+has to offer; while Code Injection is only limited by the language used. The risk from Code Injection if that,
+if the attack is successful, this can lead to loss of data, confidentiality and loss of availability.
+
 \subsection{Account Sales}
@@
 \subsubsection{Mirrored server design}
+The general idea for this is that all client functionality runs either solely on the server
+or alternatively, it runs synchronously between the client and a miror of the game server. This way,
+the state of the game is continously validated where the miror server uses the exact same inputs received
+to validate the results from the client game. If there is ever a discrepency, the client's game session resets 
+and thus prevents cheating by reseting the game state to the last valid state of the game. One problem that isn't so
+common is that this method requires a lot of bandwidth, storage and memory but nowadays, most of those concerns are minimal.
+
+\subsubsection{Pattern Detection/Analyze performance}
+This is a common way of detecting cheats for most online games since it rarely affects players direcly due to its 
+none invasive nature. Like normal anti virus software, some program in the game
+will scan the hard drive to find any know cheat software or cheat codes. Another is that it will analyze the statistical
+data from the player. For example, you might want to see how often a player is able to hit a certain part of the hitboxes
+of other players. If there is a statistical different greater than the expected standard deviation, there is a high chance
+that the player is cheating. However, thsi method also leads to false positive/negative. Very highly skilled players may
+get flagged as cheaters because of how good they are, while others may use cheats but in areas that aren't verified by the
+statistical data and thus be flagged as regular player.
+
+\subsubsection{Player Supervision}
+This is a more intrusive method of detection as it requires someone monitoring the player. Obviously, it is impossible
+to monitor every single player in the game but this method can be used in conjonction with Pattern detection. If a player
+is flagged, he doesn't have to be banned just yet, that could mean that someone can start reviewing that player's 
+gameplay and decide for himself whether or not that player is cheating or not. Some games have implemented player 
+supervision by allowing the community to send reports of disruptive behavior or suspected cheating. 
+Reports can include data such as screenshots, videos, and chatlogs that are then sent to the administrators of the gamef
+for review. If the player reported happens to be cheating any form of punishment can be dispensed.
 

### 2019-12-13 paper/paper.tex
Update paper.tex

@@
 \subsection{Account Sales}
+One of the more common video game hacks is account selling. This isn't giving
+a player an unfair advantage but selling hacked accounts to people. It is not 
+too uncommon to see somone's account information for sale on hackforums 
+without their knowledge. Selling accounts can be a lucrative business and gaining
+access to accounts through techniques such as phishing is not the most difficult
+form of hacking out there. Given Fortnite's popularity with people under 18, we
+feel the game's players are more at risk for these kinds of attacks than for
+other online games.
 
@@
  	\centering
-	\includegraphics[width = .4\linewidth]{ThreadCount}
+	\includegraphics[width = .4\linewidth]{ThreadCount.png}
 	\caption{Thread Count}
@@
  	\centering
-	\includegraphics[width=.4\linewidth]{CommentCount}
+	\includegraphics[width=.4\linewidth]{CommentCount.png}
 	\caption{Comment Count}

### 2019-12-13 paper/paper.tex
More sections

--- 2019-12-13 paper/paper.tex
@@
   \city{Cleveland}
-  \country{Ohio}}
+  \country{USA}}
 \email{eil11@case.edu}
@@
   \city{Cleveland}
-  \country{Ohio}}
+  \country{USA}}
 \email{clh137@case.edu}
@@
   \city{Cleveland}
-  \country{Ohio}}
+  \country{USA}}
 \email{mhs126@case.edu}
@@
   \city{Cleveland}
-  \country{Ohio}}
+  \country{USA}}
 \email{aas182@case.edu}
@@
   a webscraping tool to collect large amounts of data from a hacker forum to 
-  analyze key distributers in the economy.
+  analyze key distributers in the economy. After analyzing approximately 7000
+  comments and 113 threads posted on the forum, the authors found that 
+  crimeware called "Aimbots" and the CaaS (Crimeware-as-a-Service) "Account Sales"
+  were the most common things for sale in the Hack Forums marketplaces. The 
+  authors propose several solutions that the developers can implement to 
+  combat the proliferation of underground economy dealing in Fortnite exploits.
 \end{abstract}
@@
 
-[DISCUSS OUR TECHNIQUE OF DATA ANALYSIS - i.e, sentiment analyze all, then manually confirm other details]
-
 However, the data analysis for sentiment does not always apply to the comment.
@@
 
-% The title of your work should use capital letters appropriately -
-% \url{https://capitalizemytitle.com/} has useful rules for
-% capitalization. Use the {\verb|title|} command to define the title of
-% your work. If your work has a subtitle, define it with the
-% {\verb|subtitle|} command.  Do not insert line breaks in your title.
+After executing our web scraping suite of programs, we successfully collected
+a large amount of data within the following parameters. Each thread we scraped
+had to have a minimum of 30 replies to the topic, ensuring that only intensely
+discussed crimeware and CaaS would be analyzed.
 
-% If your title is lengthy, you must define a short version to be used
-% in the page headers, to prevent overlapping text. The \verb|title|
-% command has a ``short title'' parameter:
-% \begin{verbatim}
-%   \title[short title]{full title}
-% \end{verbatim}
-
-% Above was too helpful to uncomment
-[RAW RESULTS DATA, THEN REFINED DATA]
-[TABLES WOULD BE HELPFUL HERE]
+The program successfully searched Hack Forums and found 126 threads with a total
+of 7994 comments. About half of these were video game cheats crimewarea, and the
+other half was Account Sales and in-game currency sales. However, a few threads 
+were ultimated not related to our research. For example, a user had posted
+threads advertising their livestreamed playing of Fortnite. It did not have
+any relation to crimeware. Additionally, our scraper extracted a few general
+discussion threads of people arguing about the game. When we filtered from our
+data these threads and their respective comments, about 900 comments were deemed
+irrelevant from a total of 13 threads.
 
@@
 \section{Conclusion}
-[CONCLUDE]
-[ALSO DISCUSS WHAT WE LEARNED (I think she wants that...)]
-
-% Information on how to make tables
-
-% \section{Tables}
-
-% The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-% package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-% high-quality tables.
-
-% Table captions are placed {\itshape above} the table.
-
-% Because tables cannot be split across pages, the best placement for
-% them is typically the top of the page nearest their initial cite.  To
-% ensure this proper ``floating'' placement of tables, use the
-% environment \textbf{table} to enclose the table's contents and the
-% table caption.  The contents of the table itself must go in the
-% \textbf{tabular} environment, to be aligned properly in rows and
-% columns, with the desired horizontal and vertical rules.  Again,
-% detailed instructions on \textbf{tabular} material are found in the
-% \textit{\LaTeX\ User's Guide}.
-
-% Immediately following this sentence is the point at which
-% Table~\ref{tab:freq} is included in the input file; compare the
-% placement of the table here with the table in the printed output of
-% this document.
-
-% \begin{table}
-%   \caption{Frequency of Special Characters}
-%   \label{tab:freq}
-%   \begin{tabular}{ccl}
-%     \toprule
-%     Non-English or Math&Frequency&Comments\\
-%     \midrule
-%     \O & 1 in 1,000& For Swedish names\\
-%     $\pi$ & 1 in 5& Common in math\\
-%     \$ & 4 in 5 & Used in business\\
-%     $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-%   \bottomrule
-% \end{tabular}
-% \end{table}
-
-% To set a wider table, which takes up the whole width of the page's
-% live area, use the environment \textbf{table*} to enclose the table's
-% contents and the table caption.  As with a single-column table, this
-% wide table will ``float'' to a location deemed more
-% desirable. Immediately following this sentence is the point at which
-% Table~\ref{tab:commands} is included in the input file; again, it is
-% instructive to compare the placement of the table here with the table
-% in the printed output of this document.
-
-% \begin{table*}
-%   \caption{Some Typical Commands}
-%   \label{tab:commands}
-%   \begin{tabular}{ccl}
-%     \toprule
-%     Command &A Number & Comments\\
-%     \midrule
-%     \texttt{{\char'134}author} & 100& Author \\
-%     \texttt{{\char'134}table}& 300 & For tables\\
-%     \texttt{{\char'134}table*}& 400& For wider tables\\
-%     \bottomrule
-%   \end{tabular}
-% \end{table*}
-
-% In case we want to add figures to our paper
-% \section{Figures}
-
-% The ``\verb|figure|'' environment should be used for figures. One or
-% more images can be placed within a figure. If your figure contains
-% third-party material, you must clearly identify it as such, as shown
-% in the example below.
-% % \begin{figure}[h]
-% %   \centering
-% %   \includegraphics[width=\linewidth]{sample-franklin}
-% %   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-% %     Ewing, Inc. [Public domain], via Wikimedia
-% %     Commons. (\url{https://goo.gl/VLCRBB}).}
-% %   \Description{The 1907 Franklin Model D roadster.}
-% % \end{figure}
-
-% Your figures should contain a caption which describes the figure to
-% the reader. Figure captions go below the figure. Your figures should
-% {\bfseries also} include a description suitable for screen readers, to
-% assist the visually-challenged to better understand your work.
-
-% Figure captions are placed {\itshape below} the figure.
-
-% \subsection{The ``Teaser Figure''}
-
-% A ``teaser figure'' is an image, or set of images in one figure, that
-% are placed after all author and affiliation information, and before
-% the body of the article, spanning the page. If you wish to have such a
-% figure in your article, place the command immediately before the
-% \verb|\maketitle| command:
-% \begin{verbatim}
-%   \begin{teaserfigure}
-%     \includegraphics[width=\textwidth]{sampleteaser}
-%     \caption{figure caption}
-%     \Description{figure description}
-%   \end{teaserfigure}
-% \end{verbatim}
-
-% \section{Citations and Bibliographies}
-
-% The use of \BibTeX\ for the preparation and formatting of one's
-% references is strongly recommended. Authors' names should be complete
-% --- use full first names (``Donald E. Knuth'') not initials
-% (``D. E. Knuth'') --- and the salient identifying features of a
-% reference should be included: title, year, volume, number, pages,
-% article DOI, etc.
-
-% The bibliography is included in your source document with these two
-% commands, placed just before the \verb|\end{document}| command:
-% \begin{verbatim}
-%   \bibliographystyle{ACM-Reference-Format}
-%   \bibliography{bibfile}
-% \end{verbatim}
-% where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-% suffix, of the \BibTeX\ file.
-
-% Citations and references are numbered by default. A small number of
-% ACM publications have citations and references formatted in the
-% ``author year'' style; for these exceptions, please include this
-% command in the {\bfseries preamble} (before
-% ``\verb|\begin{document}|'') of your \LaTeX\ source:
-% \begin{verbatim}
-%   \citestyle{acmauthoryear}
-% \end{verbatim}
-
-%   Some examples.  A paginated journal article \cite{Abril07}, an
-%   enumerated journal article \cite{Cohen07}, a reference to an entire
-%   issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-%   monograph/whole book in a series (see 2a in spec. document)
-%   \cite{Harel79}, a divisible-book such as an anthology or compilation
-%   \cite{Editor00} followed by the same example, however we only output
-%   the series if the volume number is given \cite{Editor00a} (so
-%   Editor00a's series should NOT be present since it has no vol. no.),
-%   a chapter in a divisible book \cite{Spector90}, a chapter in a
-%   divisible book in a series \cite{Douglass98}, a multi-volume work as
-%   book \cite{Knuth97}, an article in a proceedings (of a conference,
-%   symposium, workshop for example) (paginated proceedings article)
-%   \cite{Andler79}, a proceedings article with all possible elements
-%   \cite{Smith10}, an example of an enumerated proceedings article
-%   \cite{VanGundy07}, an informally published work \cite{Harel78}, a
-%   doctoral dissertation \cite{Clarkson85}, a master's thesis:
-%   \cite{anisi03}, an online document / world wide web resource
-%   \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-%   \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-%   (Case 3) a patent \cite{JoeScientist001}, work accepted for
-%   publication \cite{rous08}, 'YYYYb'-test for prolific author
-%   \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-%   contain 'duplicate' DOI and URLs (some SIAM articles)
-%   \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-%   multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-%   couple of citations with DOIs:
-%   \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-%   citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-%   \cite{R} and \cite{UMassCitations}.
+The solutions that we proposed can most effectively curtail the growth of 
+crimeware and CaaS in the online video game community of Fortnite. For the game 
+to maintain a strong population of players, the proliferation of crimware must
+be addressed. No player will feel compelled to continue investing time into 
+Fortnite if cheating is unpunished and undetected. Our solutions to video game
+cheats ensure that games are fair for all players, and our solution to account
+sales inhibits the ability of cybercriminals to infiltrate and sell a legitimate
+player's account. The implementation of even a few of our solutions can greatly
+improve the player experience. And the relative ease with which our scraper was 
+implemented could be emulated by video game developers to surveil Hack Forums 
+to prepare countermeasures to new cheats.
 

### 2019-12-13 paper/paper.tex
Update paper.tex
sandboxing + corrected bib

@@
 \usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 	\caption{Thread Count}
-\end{subfigure}
+\end{subfigure}%
 \begin{subfigure}{.5\textwidth}
@@
 Dylan is not the most active user in his community, but nobody is as far reaching making him the most important key player in this community.
+
+\begin{figure}
+	\centering
+	\includegraphics[width = .5\linewidth]{DylanProduct.png}
+	\caption{Dylan's Product Advertisement}
+\end{figure}
 
@@
 for review. If the player reported happens to be cheating any form of punishment can be dispensed.
+
+\subsubsection{Sandboxing}
+Sandboxing reffers, in security, to a mechanism that allows you to separate running programs.
+This prevents most vulnerabilities from spreading throught the system.
+Since it is often used on unested or untrusted code, code injection can't propagate
+and thus can't work, preventing the cheat from ever working in the first place. 
+This also allows the commpany to avoid banning players since the cheats don't work.
 

### 2019-12-13 paper/paper.tex
Update paper.tex
Amend the CCS BS to look more official and correct

@@
 \begin{abstract}
-  [REWRITE THIS AT END]
   The growth of online video games has yielded a vast underground economy of
@@
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-% i never got this to work
 \begin{CCSXML}
@@
   <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+  <concept_id>10002951.10003260.10003277.10003279.10010847</concept_id>
+  <concept_desc>Information systems~Surfacing</concept_desc>
   <concept_significance>500</concept_significance>
@@
   <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
+  <concept_id>10010405.10010462.10010465</concept_id>
+  <concept_desc>Applied computing~Evidence collection, storage and analysis</concept_desc>
+  <concept_significance>500</concept_significance>
   </concept>
   <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
+  <concept_id>10010147.10010257.10010293.10003660</concept_id>
+  <concept_desc>Computing methodologies~Classification and regression trees</concept_desc>
+  <concept_significance>300</concept_significance>
   </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Information systems~Surfacing}
+\ccsdesc[500]{Applied computing~Evidence collection, storage and analysis}
+\ccsdesc[300]{Computing methodologies~Classification and regression trees}
 
@@
 	\centering
-	\includegraphics[width = .5\linewidth]{DylanProduct.png}
+	\includegraphics[width = .5\linewidth]{DylanProduct.png}\cite{opium}
 	\caption{Dylan's Product Advertisement}
@@
 This makes the key players less important as nobody has control over any aspect of the community.
-
-%[A table would be a nice addition here]
-%[DISCUSS THE DIFFERENT KEY MEMBERS OF THE COMMUNITY]
-%[WHICH CHEATS ARE MOST POPULAR]
 
@@
 \subsection{Account Theft}
-% [MFA (already in Fortnite) but suggest mandating it]
 Given the prominence of account theft and sales, we propose that Fortnite -
@@
 video game developers should require the usage of MFA as part of accessing one's
-account. Additionally, we suggest that video game developers create their own 
+account. According to a study from Google, adding a recovery phone number 
+reduced the prevented "100\% of automated bots, 99\% of bulk phishing attacks, 
+and 66\% of targeted attacks" in their study" \cite{google}. Although this 
+study is specific to Google's implementations and security policies, it is a 
+valuable heuristic to show how multi-factor authentication can greatly bolster
+security for a user.
+
+Additionally, we suggest that video game developers create their own 
 solution instead of relying on a simple SMS numerical code. SMS messages can be 
@@
 provide for the safety of a user's account.
-
-% [FIND STATS OF HOW IT REDUCES BREACHES]
-% https://security.googleblog.com/2019/05/new-research-how-effective-is-basic.html
 

### 2019-12-13 paper/paper.tex
Add Alexa citation

@@
 hacking, but one the most visited is Hack Forums (hackforums.net). Ranked
-second in top sites for "hacking" % (https://www.alexa.com/topsites/category/Top/Computers/Hacking), Hack Forums has several discussion boards
+second in top sites for "hacking," \cite{alexa} Hack Forums has several discussion boards
 on topics ranging from social engineering techniques to Internet-of-Things 

### 2019-12-13 paper/paper.tex
Fix header

@@
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+\acmConference[EECS349 F19]{CWRU EECS349 '19: Final Project}{December 13, 2019}{Cleveland, OH}
 

### 2019-12-14 paper/paper.tex
Update paper.tex

@@
 either positive or negative: Stochastic Gradient Descent (SGD), Naive Bayes, 
-Support Vector machines (SVC).
-Each algorithm gives each comment a probability to be either positive or negative.
-We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral.
+Support Vector machines (SVC). Each algorithm gives each comment a probability to be either positive or negative. 
+We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral. Below is a chart
+showing the percentage of comments that were deemed positive, negative and neutral.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{SentimentChart.png}
+	\caption{Sentiment Analysis Chart}
+\end{figure}
 
@@
 In the context of our project, the key players in the Fortnite hacker forums are those who have the most threads and/or comments under their names.
-We defined a user as a key player if they posted more than one thread or more than fifty comments from our 104 threads and 7932 comments.
+We defined a user as a key player if they posted more than one thread or more than fifty comments from our 126 threads and 7994 comments.
 We determined these metrics by manually analyzing the comments and threads and determining who were the minority of more active users.
@@
 
-\begin{figure}
+\begin{figure*}[h]
 \centering
-\begin{subfigure}{.5\textwidth}
+\begin{subfigure}{.25\textwidth}
  	\centering
@@
 \end{subfigure}%
-\begin{subfigure}{.5\textwidth}
+\begin{subfigure}{.25\textwidth}
  	\centering
@@
 \caption{Thread and Comment Pie Charts}
-\end{figure}
+\end{figure*}
 

### 2019-12-14 paper/paper.tex
Update paper.tex
updated paper + bib

@@
 We used 3 different machine learning techniques to classify each comment as
-either positive or negative: Stochastic Gradient Descent (SGD), Naive Bayes, 
-Support Vector machines (SVC). Each algorithm gives each comment a probability to be either positive or negative. 
+either positive or negative:
+\begin{itemize}
+  \item Stochastic Gradient Descent (SGD)
+  \begin{equation*}
+    E(w,b) = \frac{1}{n} \sum\limits_{i=1}^nL(y_i, f(x_i)) + \alpha R(w)
+  \end{equation*} \cite{SGD}
+
+  \item Naive Bayes
+  \begin{equation*}
+    \theta_yi = \frac{N_{yi} + \alpha}{N_y + \alpha n}
+    \newline
+    where\ N_yi = \sum_{x\in T} x_i\ and\ N_y = \sum\limits_{i=1}^n N_yi
+  \end{equation*}\cite{NB}
+
+  \item Support Vector machines (SVC)
+  \begin{equation*}  
+      sgn(\sum\limits_{i=1}^n y_i \alpha_i K(x_i, x) + \rho)    
+  \end{equation*}\cite{SVC}
+\end{itemize}
+
+Each algorithm gives each comment a probability to be either positive or negative. 
 We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral. Below is a chart
@@
 
-\begin{figure*}[h]
+\begin{figure}[h]
 \centering
@@
 \caption{Thread and Comment Pie Charts}
-\end{figure*}
+\end{figure}
 

### 2019-12-14 paper/paper.tex
Update paper.tex

@@
 
-Each algorithm gives each comment a probability to be either positive or negative. 
-We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral. Below is a chart
-showing the percentage of comments that were deemed positive, negative and neutral.
+Each algorithm gives each comment a probability to be either positive, negative or neutral. It also classifies whether a comment 
+involves a trade or a Q&A with the thread poster. We sum each algorithm's score and determine based on that score whether the comment is 
+positive, negative or neutral. Below are charts showing the percentage of comments that were deemed positive, negative and neutral, 
+percentage of comments involving a trade and percentage of comments with a Q&A.
 
@@
 	\includegraphics[width=.5\textwidth]{SentimentChart.png}
+	\caption{Sentiment Analysis Chart}
+\end{figure}
+
+Along with the webscraper was some manual analysis. Because we could not find out all information about a thread or comment from the
+webscraping, we had to manually enter in some data. One of the categories we had to manually analyze was the payment type for the
+product or service the poster was selling. The payments methods ranged from standard credit cards all the way to gift cards. Below is 
+a chart depicting the distribution of payment methods. Please keep in mind that not all posters stated the payment methods and some
+posts allow for more than one type.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{PaymentChart.png}
 	\caption{Sentiment Analysis Chart}
@@
  	\centering
-\begin{subfigure}{.25\textwidth}
+	\includegraphics[width = .5\linewidth]{ThreadCount.png}
+	\caption{Thread Count}
+\end{figure}
+\begin{figure}[h]
  	\centering
-	\includegraphics[width = .4\linewidth]{ThreadCount.png}
-	\caption{Thread Count}
-\end{subfigure}%
-\begin{subfigure}{.25\textwidth}
- 	\centering
-	\includegraphics[width=.4\linewidth]{CommentCount.png}
+	\includegraphics[width=.5\linewidth]{CommentCount.png}
 	\caption{Comment Count}
-\end{subfigure}
-\caption{Thread and Comment Pie Charts}
 \end{figure}

### 2019-12-14 paper/paper.tex
new paper + corrected typos

@@
 Each algorithm gives each comment a probability to be either positive, negative or neutral. It also classifies whether a comment 
-involves a trade or a Q&A with the thread poster. We sum each algorithm's score and determine based on that score whether the comment is 
+involves a trade or a Q\&A with the thread poster. We sum each algorithm's score 
+and determine based on that score whether the comment is 
 positive, negative or neutral. Below are charts showing the percentage of comments that were deemed positive, negative and neutral, 
-percentage of comments involving a trade and percentage of comments with a Q&A.
+percentage of comments involving a trade and percentage of comments with a Q\&A.
 
@@
 	\includegraphics[width=.5\textwidth]{PaymentChart.png}
-	\caption{Sentiment Analysis Chart}
+	\caption{Payment Method Chart}
 \end{figure}

### 2019-12-14 paper/paper.tex
Update paper.tex
new pdf
updated pqper + pdf

@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{DistributionFortniteAge.png}
+	\caption{Fortnite Age Distribution}
+\end{figure} \cite{distribage}
+
 \subsection{Hack Forums}
@@
 involves a trade or a Q\&A with the thread poster. We sum each algorithm's score 
-and determine based on that score whether the comment is 
-positive, negative or neutral. Below are charts showing the percentage of comments that were deemed positive, negative and neutral, 
-percentage of comments involving a trade and percentage of comments with a Q\&A.
+and determine based on that score whether the comment is positive,
+negative or neutral. Below are charts showing the percentage of comments that 
+were deemed positive, negative and neutral, percentage of comments involving a 
+trade and percentage of comments with a Q\&A. For the trade and Q\&A charts, a 
+one represents a trade or Q\&A and a zero represents no trade of Q\&A.
 
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{TradeChart.png}
+	\caption{Trade Chart}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{Q&AChart.png}
+	\caption{Q\&A Chart}
+\end{figure}
+
 Along with the webscraper was some manual analysis. Because we could not find out all information about a thread or comment from the
@@
 posts allow for more than one type.
+
+The distribution of the Sentiment Analysis chart shows that while neutral comments may take up a plurality of the comments, no sentiment
+is able to take up the majority of the overall comments. As for the positive or negative comments, while there might be more negative,
+the distribution is promising considering the data was taken from a hack forum. For the trade chart it actual gives minimal
+information. through manual thread analysis, we saw that the most common way of initiating a trade is through private messaging so while
+the number of trades does not seem like a lot, many trades could have been done outside of the thread. Last but not least is the Q\&A
+graph. This graph shows the general interest level of the community with regards to the different products and services offered. The 
+interest rate is higher than the trade rate, by a lot, but this is still not quite representative of the data as many people utilize
+private messaging for communication, though open thread questions about the product are still popular before PMing the seller.
 

### 2019-12-14 paper/paper.tex
Expand fortnite section

--- 2019-12-14 paper/paper.tex
@@
 utilize a diverse arsenal of weapons to defeat 99 other human opponents and 
-claim victory.
+claim victory. Initially, the players compete in a strikingly large play area.
+But as time elapses in the match, the size of the arena shrinks gradually. As a
+result, players will more easily combat each other in the ultimate goal of 
+surviving all other players. Fortnite is unique from video games like "Call of 
+Duty"  how it handles player progression. In the "Call of Duty" franchise of
+video games, as players defeat opponents, they earn "experience" which unlocks "levels" of
+progression. These levels unlock new weapons and abilities to enable the player 
+to intesify their customization to match the player's interests and desires. By
+comparison, at the beginning of a Fortnite match, all players start with the
+same, mediocre weapon and are tasked with exploring the gameplay arena for 
+improved equipment. Therefore, it is impossible for players to purchase an
+advantage that affects their gameplay, which raises the question of how 
+Fortnite generates revenue for Epic Games. Fortnite is a free-to-play video game, which means that there is
+no initial upfront cost to downloading and playing the game; however, Epic Games
+has monetized the game through the availablity of a store for cosmetic items. 
+These cosmetic items can only be acquired by purchasing "V-Bucks" from Epic Games.
+Cosmetic items - as the name might imply - modify the external appearance of the 
+player's avatar in a Fortnite match. Cosmetics are sometimes exclusive to 
+certain accomplishments and time periods. Because of this, an account with 
+a large collection of cosmetic items can easily have a real-world currency value
+associated with it. And for exclusive items, the rarity and inability to 
+earn these items as a later player means that these accounts are valuable. The 
+combination of exciting, fast-paced matches and unique ways to customize one's
+character avatar has helped to make Fortnite one of the most popular video games
+ever.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{DistributionFortniteAge.png}
+	\caption{Fortnite Age Distribution}
+\end{figure}
 
@@
 	\caption{Sentiment Analysis Chart}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{TradeChart.png}
+	\caption{Trade Chart}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{Q&AChart.png}
+	\caption{Q\&A Chart}
 \end{figure}

### 2019-12-14 paper/paper.tex

@@
 	\caption{Fortnite Age Distribution}
-\end{figure}
+\end{figure} \cite{distribage}
 

### 2019-12-14 paper/paper.tex
Expand web scraping section

@@
 web scraping program must be written to extract the relevant information from
-the HTML present on the page. Given the sheer volume of information that must
-be collected, the best action is to implement our own program to scrape data 
-from Hack Forums.
+the Hyptertext Markup Language (HTML) present on the page. Unfortnuately, 
+scraping the data is not as simple as traversing the pages and downloadsing the 
+web page's HTML files and manullay inspecting them. Due to the large amount of 
+threads and comments that must be analyzed, a program needs to be created to 
+find the comment texts of each page and aggregate the comments in one file. 
+And since data aggregation can be automated, the traversal of the website 
+should be too. In most cases where a functional Application Programming Interface
+(API) is not available, a web scraping program has to analyze the hyperlinks
+available on the page to identify further pages to traverse and collect data.
+Since forum style websites are neatly categorized for ease of use by visitors, 
+traversal is not complicated.
 
